The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-24 Results/analysis.tex
fixed todos in evaluation

\subsection{Analysis of the Received \Email Data}
During our analysis of the received \emails, we found that the \emails that we received belonged to one of three categories:
\begin{enumerate}
	\item \Emails with the \texttt{bcc} header successfully injected\\
	  This form of injection was our initial objective, and we found
% Adam: Sai, why isn't this number a command?
      265 such \emails in our received \emails. This validates that the web applications that sent these \emails are vulnerable to \ehi.

	\item \Emails with the \texttt{to} header successfully injected\\
	We discovered an unintended vulnerability class during our analysis, which we call \texttt{To~header injection}. These injections reflect the ability to inject any number of \email addresses into the \texttt{to} field of the SMTP message while being unable to inject any other header into the \emails. We attribute this behavior to inconsistent sanitization by the application. 
    % Adam: I can't understand what this sentence is trying to say
	The vulnerability is further aided by the leniency shown by mail servers, wherein they parsed malformed \email addresses and delivered it to the right mail server, and on the receiving end, the mail was delivered to the right mailbox.

@@

	\item \Emails with the \texttt{x-check} header successfully injected\\
    The third category of \emails received were \emails with the \texttt{x-check} header injected. As discussed in Section~\ref{analyze:detect_x_check}, 
    we can differentiate between unsuccessful attempts and successful attempts by injecting the additional header and checking whether headers other than the \texttt{bcc} header can be injected into the generated \email. 
\end{enumerate}

% Adam: Sai, we need to put the actual numbers in the text. We cannot count on the readers to look at the table (of course, we should use the commands
We list each category and the number of \emails received by the category in Table~\ref{tab:analysis}.

@@

We explain the combination of these header injections (4-7) as follows:
\begin{itemize}
	\item \Email Header Injections with \texttt{bcc} and \texttt{x-check} headers\\
	  These represent the scenario where an attacker can inject multiple headers into the \emails. We can see that over 70\% of the received \texttt{bcc} header injected \emails are also susceptible to other header injections.
      % Adam: What is the exact percentage? We should use that rather than an approximate number

@@

	\item \texttt{x-check} headers found in \texttt{nuser} \emails\\
	  In addition to analyzing the \texttt{maluser} account, we also analyze emails received by the \texttt{nuser} account.
      % Adam: Why aren't we explaining this here? It reads strange.
      We explain the presence of these headers in the following paragraph.

	\item Unique \texttt{x-check} headers found in \texttt{nuser} \emails\\
	  These represent the \emails with unique form ids that were \emph{not} already found in the \texttt{maluser} account. We attribute these \emails to (probably) having a web application that was built with Python or another language having a similar behavior with respect to constructing headers.
      % Adam: What is the actual behavior? This is confusing.

	\item Total successful injections\\
	  This represents the total number of successful injections. This includes the \ehi with \texttt{bcc} header\,(1), \texttt{To} header injections alone\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} \emails\,(7). This is the total number of vulnerabilities that were found by our system.

      % Adam: we need the actual #s here too. These are the core results of our analysis, they need to be in the text.

>>>>

\subsection{Analysis of the Received \Email Data}
During our analysis of the received \emails, we found that the \emails that we received belonged to one of three categories:
\begin{enumerate}
	\item \Emails with the \texttt{bcc} header successfully injected\\
	  This form of injection was our initial objective, and we found
% Adam: Sai, why isn't this number a command? - DONE.
      \ehibcc such \emails in our received \emails. This validates that the web applications that sent these \emails are vulnerable to \ehi.

	\item \Emails with the \texttt{to} header successfully injected\\
	We discovered an unintended vulnerability class during our analysis, which we call \texttt{To~header injection}. These injections reflect the ability to inject any number of \email addresses into the \texttt{to} field of the SMTP message while being unable to inject any other header into the \emails. We found \ehito such \emails in our received \emails. We attribute this behavior to inconsistent sanitization by the application. 
    % Adam: I can't understand what this sentence is trying to say - Removed.

@@

	\item \Emails with the \texttt{x-check} header successfully injected\\
    The third category of \emails received were \emails with the \texttt{x-check} header injected. As discussed in Section~\ref{analyze:detect_x_check}, 
    we can differentiate between unsuccessful attempts and successful attempts by injecting the additional header and checking whether headers other than the \texttt{bcc} header can be injected into the generated \email. \ehixcheck \emails were received with the \texttt{x-check} header injected.
\end{enumerate}

% Adam: Sai, we need to put the actual numbers in the text. We cannot count on the readers to look at the table (of course, we should use the commands
We list each category and the number of \emails received by that category in Table~\ref{tab:analysis}. 
We explain the combination of these header injections (4-7) as follows:

@@

\begin{itemize}
	\item \Email Header Injections with both \texttt{bcc} and \texttt{x-check} headers\\
	  These represent the scenario where an attacker can inject multiple headers into the \emails. We can see that 65.65\% of the received \texttt{bcc} header injected \emails are also susceptible to being injected with additional headers.
      % Adam: What is the exact percentage? We should use that rather than an approximate number - DONE.

@@

	\item Total \texttt{x-check} headers and unique \texttt{x-check} headers found in \texttt{nuser} \emails\\
		We found a total of \ehinuserxcheck \emails in the \texttt{nuser} account. Out of these, \ehiuniquenuserxcheck had unique form ids that were \emph{not} already found in the \texttt{maluser} account. We attribute these \emails to (probably) being sent by a web application that was built with Python or another language having a similar behavior with respect to ignoring duplicate headers while constructing an \email, thus appending the \texttt{x-check} header and \emph{not} the \texttt{bcc} header. 
      % Adam: What is the actual behavior? This is confusing. - Changed. DONE.

	\item Total successful injections\\
	  This represents the total number of successful injections. This includes the \ehi with \texttt{bcc} header\,(1), \texttt{To} header injections alone\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} \emails\,(7). A total of \success vulnerabilities were found by our system.

      % Adam: we need the actual #s here too. These are the core results of our analysis, they need to be in the text. - DONE.

### 2016-05-24 Results/data_analysis.tex
Edited through the results section
fixed todos in evaluation

\begin{table*}[!htbp]
	\centering
	\begin{tabular}{|l|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Type of Injection}} &
		\multicolumn{1}{p{3cm}|}{\centering \textbf{No. of e-mails received}}\\
		\hline
		E-Mail Header Injections with \texttt{bcc} header & 304\\
		\hline
		E-Mail Header Injections with \texttt{x-check} header & 252\\
		\hline
		\texttt{To header} injections alone & 157\\
		\hline
		E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers & 216\\
		\hline
		Both \texttt{To header} injections and x-check headers &
		12\\
		\hline
		\texttt{x-check} headers found in \texttt{nuser} e-mails & 67\\
		\hline
		Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & 35\\
		\hline
		Total successful injections (1 + 3 + 7) & 496\\

>>>>

\begin{table*}[tbp]
	\centering
	\begin{tabular}{|l|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Type of Injection}} &
		\multicolumn{1}{p{3cm}|}{\centering \textbf{No. of e-mails received}}\\
		\hline
		E-Mail Header Injections with \texttt{bcc} header & \ehibcc \\
		\hline
		E-Mail Header Injections with \texttt{x-check} header & \ehixcheck \\
		\hline
		\texttt{To header} injections alone & \ehito \\
		\hline
		E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers & \ehibccxcheck \\
		\hline
		Both \texttt{To header} injections and x-check headers &
		\ehitoxcheck \\
		\hline
		\texttt{x-check} headers found in \texttt{nuser} e-mails & \ehinuserxcheck \\
		\hline
		Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & \ehiuniquenuserxcheck \\
		\hline
		Total successful injections (1 + 3 + 7) & \success \\

### 2016-05-24 Results/disclosure.tex
fixed todos in evaluation

\subsection{Responsible Disclosure of Discovered Vulnerabilities}
After we discovered an \ehi vulnerability on a particular website, we attempted to notify the developers of the vulnerable web application, along with a brief description of the vulnerability.
We chose to \email the following mailboxes, following the rules specified in RFC~2142~\cite{rfc2142}:
% Adam: don't we use \texttt for all the email addresses in the paper? We should use the same thing here
\begin{itemize}
	\item security@domain.com - Used for Security bulletins or queries.
	\item admin@domain.com - Used to contact the administrator of a website.
	\item webmaster@domain.com - Synonym for administrator, same functionality as admin.
\end{itemize}

% Adam: sai, is this number up-to-date? 
Out of the \domains\ vulnerable domains found, only 108 websites had the mailboxes able to receive \emails. For the remaining domains, we used the \texttt{whois}~\cite{whois} data to find the contact details of the owner, then we \emailed. The number of emails we sent and the number of developer responses we received is shown in Table~\ref{tab:devresp}.

\begin{table}[tbp]
\centering
\begin{tabular}{|c|c|c|}
	\hline
	\multicolumn{1}{|p{2cm}}{\centering \textbf{Notified websites}} &
	\multicolumn{1}{|p{2cm}|}{\centering \textbf{Developer Responses}} &
	\multicolumn{1}{p{2cm}|}{\centering \textbf{Confirmed discoveries}}\\
	\hline
	\domains\ & 13 & 9 \\
	\hline
\end{tabular}
	\caption[\titlecap{}]{Responsible disclosure of the discovered vulnerabilities to developers and the number of received responses.}
	\label{tab:devresp}
\end{table}

% Adam: did we get updated notifications?
We received 13 developer responses, confirming 9 discovered vulnerabilities. Two of the developers fixed the vulnerability on their website.
% is this done?
From our research, it is clear that \ehi is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on. This value acts as a \emph{lower bound} for prevalence of \ehi vulnerability, and can quite easily be larger if the attacks were broader, crafted for the individual web application, and  less automated.

>>>>

\subsection{Responsible Disclosure of Discovered Vulnerabilities}
After we discovered an \ehi vulnerability on a particular website, we attempted to notify the developers of the vulnerable web application, along with a brief description of the vulnerability.
We chose to \email the following mailboxes, following the rules specified in RFC~2142~\cite{rfc2142}:
% Adam: don't we use \texttt for all the email addresses in the paper? We should use the same thing here - DONE.
\begin{itemize}
	\item \texttt{security@domain.com} - Used for Security bulletins or queries.
	\item \texttt{admin@domain.com} - Used to contact the administrator of a website.
	\item \texttt{webmaster@domain.com} - Synonym for administrator, same functionality as admin.
\end{itemize}

% Adam: sai, is this number up-to-date? 
Out of the \domains\ vulnerable domains found, only \emailedDefaultmailbox websites had the mailboxes able to receive \emails. For the remaining domains, we used the \texttt{whois}~\cite{whois} data to find the contact details of the owner and then \emailed them. The number of emails we sent and the number of developer responses we received is shown in Table~\ref{tab:devresp}.

\begin{table}[tbp]
\centering
\begin{tabular}{|c|c|c|}
	\hline
	\multicolumn{1}{|p{2cm}}{\centering \textbf{Notified websites}} &
	\multicolumn{1}{|p{2cm}|}{\centering \textbf{Developer Responses}} &
	\multicolumn{1}{p{2cm}|}{\centering \textbf{Confirmed discoveries}}\\
	\hline
	\domains\ & \responses & \confirmed \\
	\hline
\end{tabular}
	\caption[\titlecap{}]{Responsible disclosure of the discovered vulnerabilities to developers and the number of received responses.}
	\label{tab:devresp}
\end{table}

% Adam: did we get updated notifications? - nope. DONE.
We received \responses developer responses, confirming \confirmed discovered vulnerabilities. Two of the developers fixed the vulnerability on their website.
% is this done? 1 additional email asking for more information, but no confirmation.
From our research, it is clear that \ehi is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on. This value acts as a \emph{lower bound} for prevalence of \ehi vulnerability, and can quite easily be larger if the attacks were broader, crafted for the individual web application, and  less automated.

### 2016-05-24 Results/pre_result.tex
fixed todos in evaluation

% TODO: Need to put in a number here, and discuss the high level
% crawl. 
We ran the system for XYZ days/hours/whatever

From our extensive crawl of the web, we were able to gather the data
shown in Table~\ref{tab:data}. Our system crawled \urls unique URLs,
found a total of \forms\ forms from \uniqueforms\ unique domains, and
found \emailforms\ forms that contained an \email field from \uniqueemailforms\ unique domains.

>>>>

% TODO: Need to put in a number here, and discuss the high level
% crawl. - DONE

From our extensive crawl of the web, we were able to gather the data
shown in Table~\ref{tab:data}. We ran the system for 76 days, during which our system crawled \urls unique URLs,
and found a total of \forms\ forms from \uniqueforms\ unique domains. Out of these forms, our system
found \emailforms\ forms that contained an \email field, from \uniqueemailforms\ unique domains.
